Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-10-16 analysis/paper/paper.Rmd
improve table 1 formatting

knitr::kable(tbl,caption="Monitoring scenario parameters.")
```

>>>>

tbl <- tbl %>% separate_wider_delim(name, names = c("symbol", "name"), delim = ", ") %>% 
  select(-name, symbol, units, description, values)

knitr::kable(tbl,caption="Monitoring scenario parameters and values used in simulations.",
             col.names = str_to_title(colnames(tbl)))
```
